Collaborative Visual Analysis on the Web with RCloud

### 2015-06-25 introduction.tex
merge

Fortunately, there is abundant evidence that technology can
solve many of these problems.
Gutierrez collected interviews with data scientists~\cite{Gutierrez:2014:DSA},
which include the following:

@@

In view of the opportunity to improve this situation,
we created a software environment that supports the end-to-end
visual analytics process for individuals and teams and
their work within larger organizations.

In this paper, we contribute the design of RCloud, and an
interview study based on its development and deployment
at AT\&T Labs for about three years.

@@

For the most part, the improved capabilities are available by default,
without much explicit involvement on the part of
data scientists and other customers. Visual analytics experiments are
conveniently shared and turned into production websites, without moving
or porting code. All the published artifacts in the system can be
searched immediately. Recommendation is as easy as clicking a star
on a useful notebook.

The high level architecture of the prototype system
is shown in figure~\ref{fig:system}.
We chose R as the foundation because it is already
the dominant statistical computing language in our lab.
R also has many useful packages for data analysis and visualization,
and the core system and its packages are open source that can be modified to
support research.

Over the past three years, we prototyped RCloud and deployed it to
a community of data scientists, business analysts and other colleagues. The
platform today has over 300 active accounts; about 20 people use it regularly,
another 30 people use it more than once a week, and another 50 use it more than
once a month. Most of the
active users are members of AT\&T Labs, but some are data scientists and other
collaborators in other business units.

>>>>

Fortunately, there is abundant evidence that technology can
solve many of these problems.
Gutierrez's interviews with data scientists~\cite{Gutierrez:2014:DSA}, 
include the following:

@@

In order to tackle these issues, we created RCloud, a software environment
supporting the end-to-end visual analytics process for individuals and
teams and their work within larger organizations. In this paper, we
contribute the design of RCloud, and an interview study based on the
course of its development and deployment at AT\&T Labs for about three
years.

@@

One of the key design criteria for RCloud was \emph{transparency}: for
the most part, the novel features are
available and usable by default, without explicit involvement on the part of
data scientists and other customers. Visualizations are
shared and turned into production websites without moving
or porting code; all artifacts present in the system can be
searched at all times; recommendation is as easy as clicking a star
on a useful workbook.

The high level architecture of RCloud
is shown in figure~\ref{fig:system}.
We chose R as the foundation because it is already
the dominant statistical computing language in our lab.
R also has many useful packages for data analysis and visualization,
and the core system and its packages are open source that can be modified to
support research.

Over the past three years, we prototyped RCloud and deployed it to
a community of data scientists, business analysts and other colleagues. The
platform today has over 300 active accounts; about 20 people use it regularly,
another 30 people use it more than once a week, and another 50 use it more than
once a month. Most of the
active users are members of AT\&T Labs, but some are data scientists and
collaborators in other business units.
